The Concurrent Calculi Formalisation Benchmark

### 2023-10-09 paper/paper.tex
Fix outdated description of coinduction challenge.

\subsection{Coinduction}
Our \textbf{coinduction challenge} (Appendix~\ref{sec:challenge:coinduction}) is to prove that strong barbed bisimulation is an equivalence relation \footnote{AM: this seems wrong, see:  \( \sbcong{P}{Q} \) if and only if for any process \( R \) and substitution \( \sigma \), \( \sbbisim{\Ppar{\applysubst{\sigma}{P}}{R}}{\Ppar{\applysubst{\sigma}{Q}}{R}} \).}for an untyped calculus of communicating systems with (infinite) replication of processes.
The proof involves reasoning coinductively about the infinite behaviours of the replication operator.
We invite anyone interested to send us solutions to the challenge problems and to publish experience reports detailing the advantages and disadvantages of their approaches.

>>>>

\subsection{Coinduction}
Our \textbf{coinduction challenge} (Appendix~\ref{sec:challenge:coinduction}) is to prove that strong barbed congruence acts like a congruence for an untyped calculus of communicating systems with (infinite) replication of processes.
The proof involves reasoning coinductively about the infinite behaviours of the replication operator.
We invite anyone interested to send us solutions to the challenge problems and to publish experience reports detailing the advantages and disadvantages of their approaches.
